Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-08 ms_pre_post.Rmd
Add second section of the results

Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs. We can therefore use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A). In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$).

>>>>

Figure 1 shows changes in mean allele values of tendency for polyandry, inbreeding mating strategy, and inbreeding fertilisation strategy across all eight possible combinations of costs. In Figure 1A, when no phenotypes are costly, inbreeding mating strategy and inbreeding fertilisation strategy evolve to inbreeding avoidance ($M_{a}<0$ and $F_{a}<0$), and females evolve to be polyandrous ($P_{a}>0$). Costs of phenotypes have a direct effect on evolution, causing inbreeding mating strategy and inbreeding fertilisation strategy phenotypes to evolve to values closer to zero (because realisation of inbreeding strategy costs increases with phenotype absolute values) and tendency for polyandry phenotypes to evolve to values that are more negative (because realisation of polyandry costs increases with positive phenotype values).

We can use Figure 1 to test the hypothesis that inbreeding mating strategy will evolve to inbreeding avoidance ($M_{a}<0$), but inbreeding fertilisation strategy will be negligible ($F_{a} \approx 0$) when mating costs are low ($c_{M}=0$) relative to the costs of tendency for polyandry and inbreeding fertilisation strategy ($c_{P}=0.02$ or $c_{F}=0.02$) by comparing different cost combinations to the null model in which all costs equal zero (Figure 1A). Figures 1A,C,D,G show that inbreeding avoidance evolves at a comparable rate whenever $c_{M}=0$. However, inbreeding fertilisation strategy is never negligible; $F_{a}$ values are still negative over generations even when costs of inbreeding mating strategy is weak and costs of tendency for polyandry and inbreeding fertilisation strategy are strong.

We can also use Figure 1 to test the hypothesis that inbreeding fertilisation strategy will evolve to inbreeding avoidance ($F_{a}<0$), but inbreeding mating strategy will be negligible ($M_{a} \approx 0$) when tendency for polyandry and inbreeding fertilisation strategy costs are low ($c_{P}=0$ and $c_{F}=0$) relative to the cost of inbreeding mating strategy ($c_{M}=0.02$). Figure 1B shows that inbreeding avoidance through fertilisation bias evolves ($F_{a}<0$) under these conditions, but evolution of inbreeding mating strategy is not negligible; $M_{a}$ values are consistently negative across all combinations of costs.

<!--- Interestingly, a high cost of only tendency for polyandry (Figure 1C) or only inbreeding fertilisation strategy (Figure 1D) shows how these phenotypes are evolutionarily tied such that a cost of one phenotype can feed back to affect evolution of the other phenotype. For example, Figure 1C shows simulations in which inbreeding fertilisation strategy is not costly, causing $F_{a}$ values to become more negative (stronger inbreeding avoidance) than when both inbreeding fertilisation strategy and tendency for polyandry are costly (Figure 1G). However, $F_{a}$ values are not as negative as they would be if neither tendency for polyandry or inbreeding fertilisations trategy were costly (Figure 1A) because expression of fertilisation bias was hindered by costs of polyandry and an associated reduction in evolved mating frequency. Similarly, Figure 1D shows simulations in which only inbreeding fertilisation strategy was costly, causing less strong inbreeding avoidance through fertilisation bias. Consequently, tendency for polyandry values were lower than when inbreeding fertilisation strategy was not costly (Figure 1A) because polyandry was less beneficial when it did not result in strong inbreeding avoidance through fertilisation bias. --->
